\( \tool \): JavaScript IR-based Semantics Extraction Toolchain

### 2019-08-24 icse20/compiler.tex
Updated image for fault localizer
fix to fault localizer
Second submission

\section{Algorithm Compiler}\label{sec:compiler}
\begin{figure}
  \centering
  \includegraphics[width=0.5\textwidth]{img/algo_compiler.png}
  \caption{Overall structure of {\sf Algorithm Compiler}}
  \label{fig:algo-compiler}
\end{figure}

@@

To diagnose the root cause of parsing failures, we support a \textsf{Fault Localizer},
which takes not-yet-convertible steps dubbed ``failed steps'' as arguments.
The basic idea is to check whether we can parse the failed algorithm step
with the assumption that a specific sub-sequence of the
failed step is successfully parsed.  We define a \textit{rule suggestion}
as such sub-sequence of failed steps with the name of an existing compile rule.
\textsf{Fault Localizer} refines candidates of rule suggestions into
most specific ones. This approach was actually helpful for us when we update existing
compile rules for new versions of the specification.

>>>>

\section{Algorithm Compiler}\label{sec:compiler}
\begin{figure}
  \centering
  \includegraphics[width=0.48\textwidth]{img/algo_compiler.png}
  \caption{Overall structure of {\sf Algorithm Compiler}}
  \label{fig:algo-compiler}
\end{figure}

@@

To diagnose root causes of parsing failures, we support a \textsf{Fault Localizer},
which takes not-yet-convertible steps dubbed ``failed steps'' as arguments.
The basic idea is to check whether we can parse the failed algorithm step
with the assumption that a specific sub-sequence of the
failed step is successfully parsed.  We define a \textit{rule suggestion}
as such a sub-sequence of failed steps with the name of an existing compile rule.
\textsf{Fault Localizer} refines candidates of rule suggestions into the
most specific ones. It helped us when we update existing
compile rules for new versions of the specification.

### 2019-08-24 icse20/related.tex
Second submission

Several approaches have defined the formal semantics of JavaScript.
\citet{lambdajs} defined a core calculus of JavaScript, and expressed the
rest as desugaring.  While it presents the core JavaScript semantics in
an extension of the $\lambda$ calculus, it does not show the semantics
correspondence defined in the ECMAScript specification.  KJS~\cite{kjs} and
JaVerT~\cite{javert} defined formal semantics of JavaScript by manually converting
the ECMAScript specification to their own formal languages.  KJS mapped
ECMAScript 5.1 in the K framework~\cite{kframework}, which can be used
for program verification and analysis.  Similarly, JaVerT converts the
specification to their own IR called JSIL to make further analysis.
Our approach provides a mechanized framework to synthesize syntactic parsers and
to automatically extract semantics
using rule-based compilation technique. It significantly reduces human
efforts and also flexible for future specification updates.

>>>>

Several approaches have defined the formal semantics of JavaScript.
\citet{lambdajs} defined a core calculus of JavaScript, and expressed the
rest as desugaring.  While it presents the core JavaScript semantics in
an extension of the $\lambda$ calculus, it does not show the semantics
correspondence defined in the ECMAScript specification.  KJS~\cite{kjs} and
JaVerT~\cite{javert} defined formal semantics of JavaScript by manually converting
the ECMAScript specification to their own formal languages.  KJS mapped
ECMAScript 5.1 in the K framework~\cite{kframework}, which can be used
for program verification and analysis.  Similarly, JaVerT converts the
specification to their own IR called JSIL to make further analysis.
Our approach provides a mechanized framework to synthesize syntactic parsers and
to automatically extract semantics
using a rule-based compilation technique, which significantly reduces human
efforts.
